Testing specification of baseline models

### 2023-03-09 analysis/analysis_spec_tests.Rmd
Correct error in spec test

marg_prob_alt |>
  gt() |>
  fmt_percent(2:7, decimals = 3) |>
  cols_label(race="Race", baseline="No Covariates", year_dummy="Year treated as dummy", 
             year_linear="Year treated as linear", year_dummy_interact="Year (dummy) x Grade",
             year_linear_interact="Year (linear) x Grade", 
             year_grade_stat="Year (linear) x Grade and State") |>
  tab_source_note("*Notes*: All models except no covariate case include dummies for current grade and state") |>
  tab_spanner("Sensitivity tests on calendar year x grade coding", 3:7)

>>>>

marg_prob_alt |>
  gt() |>
  fmt_percent(2:7, decimals = 3) |>
  cols_label(race="Race", baseline="No Covariates", year_dummy="Year treated as dummy", 
             year_linear="Year treated as linear", year_dummy_interact="Year (dummy) x Grade",
             year_linear_interact="Year (linear) x Grade", 
             year_grade_state="Year (linear) x Grade and State") |>
  tab_source_note("*Notes*: All models except no covariate case include dummies for current grade and state") |>
  tab_spanner("Sensitivity tests on calendar year x grade coding", 3:7)
